IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/retrofit.tex
minor

We note that our embedding corresponds to the lump embedding
of~\cite{Matthews:2007:OSM:1190216.1190220}, terms in one language are
treated opaquely in the other.
%
Indeed since our embedding is defined for an arbitrary language |targetLang|,
we cannot do better.
%
However, when we have more information about the target language, it is
possible to add rules for a natural embedding of expressions that occur in both
languages.  In our specific example with |targetLangML|, we can choose to
preserve booleans across language boundaries as follows:
\begin{mathpar}
\inferrule
{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
\and
\inferrule
{ |b member {true, false}| } {| intE (TI b) -> intE b |}
\end{mathpar}

>>>>

We note that our embedding corresponds to the lump embedding
of~\cite{Matthews:2007:OSM:1190216.1190220} where terms in one language are
treated opaquely in the other.
%
Indeed since our embedding is defined for an arbitrary language |targetLang|,
we cannot do better.
%
However, when we have more information about the target language, it is
possible to add rules for a natural embedding of expressions that occur in both
languages.  In our specific example with |targetLangML|, we can choose to
preserve booleans across language boundaries as follows:
\begin{mathpar}
\inferrule
{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
\and
\inferrule
{ |b member {true, false}| } {| intE (TI b) -> intE b |}
\end{mathpar}
